Deciding to Disclose: A Decision Theoretic Agent Model of Pregnancy and Alcohol Misuse

### 2014-12-31 Model.tex
Springer styles

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=\textwidth]{figures/rounded_clover_infosets}
\end{adjustbox}
\caption{Simplified game tree. Green, blue, and orange arrows correspond to moves by nature, women, and midwives, respectively. Green terminal nodes indicate that the game may repeat from that point, and black nodes are exits.}

@@

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=0.43\paperwidth]{figures/tree_zoom}
\end{adjustbox}
\caption{Detail view of a single game tree branch, showing the possible moves by each player, with information sets for midwives.}

@@

\begin{figure}[H]
\begin{adjustbox}{center}\subfloat[Women]{\includegraphics[width=0.43\paperwidth]{figures/women_influence}

}\subfloat[Midwives]{\includegraphics[width=0.43\paperwidth]{figures/mw_influence}}\end{adjustbox}
\caption{Influence diagrams, showing the game broken into two decision problems.}

>>>>

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=119mm]{figures/rounded_clover_infosets}
\end{adjustbox}
\caption{Simplified game tree. Arrows correspond to two moves by nature, followed by women, and midwives respectively. Light terminal nodes indicate that the game may repeat from that point, and black nodes are exits.}

@@

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=119mm]{figures/tree_zoom}
\end{adjustbox}
\caption{Detail view of a single game tree branch, showing the possible moves by each player, with information sets for midwives.}

@@

\begin{figure}[H]
\begin{adjustbox}{center}\subfloat[Women]{\includegraphics[width=119mm]{figures/women_influence}}\end{adjustbox}
\vskip
\begin{adjustbox}{center}\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}\end{adjustbox}
\caption{Influence diagrams, showing the game broken into two decision problems.}

### 2014-12-31 disclosure_game.tex
Tables, switched to input rather than include
Because nesting
Bit more on results
Ammendments
Incorporating Seth & Jakub's comments
More comments
PDF figures
Springer styles

\documentclass{article}
\usepackage{tikz}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{ifthen}
\newboolean{enable-backrefs} % enable backrefs in the bibliography
\setboolean{enable-backrefs}{true} % true false
\newcommand{\backrefnotcitedstring}{\relax}%(Not cited.)
\newcommand{\backrefcitedsinglestring}[1]{(Cited on page~#1.)}
\newcommand{\backrefcitedmultistring}[1]{(Cited on pages~#1.)}
\ifthenelse{\boolean{enable-backrefs}}%
{%
		\PassOptionsToPackage{hyperpageref}{backref}
		\usepackage{backref} % to be loaded after hyperref package
		   \renewcommand{\backreftwosep}{ and~} % separate 2 pages
		   \renewcommand{\backreflastsep}{, and~} % separate last of longer list
		   \renewcommand*{\backref}[1]{}  % disable standard
		   \renewcommand*{\backrefalt}[4]{% detailed backref
		      \ifcase #1 %
		         \backrefnotcitedstring%
		      \or%
		         \backrefcitedsinglestring{#2}%
		      \else%
		         \backrefcitedmultistring{#2}%
		      \fi}%
}{\relax}
\usepackage{fullpage}
\usepackage{comment}
\usepackage{natbib}
\setcitestyle{authoryear,round,aysep={,}}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[subrefformat=parens,labelformat=parens]{subfig}
\usepackage[nolist,smaller]{acronym}
\usepackage{nomencl}
\usepackage[style=long,nolist]{glossaries}

\title{Deciding to Disclose: Pregnancy and Alcohol Misuse}
\author{Jonathan Gray \and Jakub Bijak \and Seth Bullock\\
University of Southampton, Southampton, SO17 1BJ, United Kingdom\\
E-mail: \texttt{j.gray@soton.ac.uk}}
\date{\vspace{-5ex}}
\begin{document}
\maketitle

%*************************
% Acronyms
%*************************
%\phantomsection
%\refstepcounter{dummy}
\pdfbookmark[1]{Acronyms}{acronyms}
%\markboth{\spacedlowsmallcaps{Acronyms}}{\spacedlowsmallcaps{Acronyms}}
%\section*{Acronyms}
\begin{acronym}[UML]
  \acro{FAS}{Foetal Alcohol Syndrome}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{PT}{Prospect Theory}
  \acro{NICE}{National Institute for Health and Care Excellence}
  \acro{IAPT}{Improving Access to Psychological Therapies}
  \acro{CMACE}{Centre for Maternal and Child Enquiries}
  \acroindefinite{CMACE}{the}{the}
  \acro{AUDIT}{Alcohol Use Disorders Identification Test}
  \acro{T-ACE}{Tolerance, Annoyance, Cut down, Eye-opener}
  \acro{RCOG}{Royal College of Obstetricians and Gynecologists}
  \acroindefinite{RCOG}{the}{the}
  \acro{AML}{acute myeloid leukemia}
  \acro{ADHD}{Attention Defecit Hyperactivity Disorder}
  \acro{PND}{Postnatal Depression}
  \acro{RCT}{randomised control trial}
  \acro{WHO}{the World Health Organisation}
  \acro{ESS}{Evolutionarily Stable Strategy}
  \acro{MCMC}{Markov chain monte carlo methods}
  \acro{DU}{Discounted Utility}
  \acro{AIC}{Akaike information criterion}
  \acro{ANOVA}{analysis of variance}
  \acro{ALSPAC}{the Avon Longitudinal Study of Parents and Children}
  \acro{GEM}{Gaussian Emulation Machine}
  \acrodefplural{GEM}{Gaussian Emulation Machines}
  \acro{GEM-SA}{Gaussian Emulation Machine for Sensitivity Analysis}
  \acro{JIT}{Just-in-time}
  \acro{ABM}{Agent Based Modelling}
  \acro{ABMs}{Agent Based Models}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{FFH}{Fast and Frugal Heuristic}
  \acro{OFC}{orbito-frontal cortex}
  \acro{BACCO}{Bayesian Analysis of Computer Code Outputs}
\end{acronym}

@@

%\refstepcounter{dummy}
\pdfbookmark[1]{Glossary}{glossary}
\printglossary[type=main]

\printnomenclature{}

@@

\include{Abstract}
\acresetall

\include{Introduction} %(half page)

\include{Background}

\include{Model}

\include{Methods}

\include{Results}

\include{Conclusion}
\include{Acknowledgements}

\bibliography{library,library_addendum}
\bibliographystyle{myplainnat}

\appendix

\include{SensitivityAnalysis}
\end{document}

>>>>

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}

% choose options for [] as required from the list
% in the Reference Guide

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{tikz}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{ifthen}
\usepackage{csquotes}
\newboolean{enable-backrefs} % enable backrefs in the bibliography
\setboolean{enable-backrefs}{true} % true false
\newcommand{\backrefnotcitedstring}{\relax}%(Not cited.)
\newcommand{\backrefcitedsinglestring}[1]{(Cited on page~#1.)}
\newcommand{\backrefcitedmultistring}[1]{(Cited on pages~#1.)}
\ifthenelse{\boolean{enable-backrefs}}%
{%
		\PassOptionsToPackage{hyperpageref}{backref}
		\usepackage{backref} % to be loaded after hyperref package
		   \renewcommand{\backreftwosep}{ and~} % separate 2 pages
		   \renewcommand{\backreflastsep}{, and~} % separate last of longer list
		   \renewcommand*{\backref}[1]{}  % disable standard
		   \renewcommand*{\backrefalt}[4]{% detailed backref
		      \ifcase #1 %
		         \backrefnotcitedstring%
		      \or%
		         \backrefcitedsinglestring{#2}%
		      \else%
		         \backrefcitedmultistring{#2}%
		      \fi}%
}{\relax}
\usepackage{fullpage}
\usepackage{comment}
\usepackage{natbib}
\setcitestyle{authoryear,round,aysep={,}}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[subrefformat=parens,labelformat=parens]{subfig}
\usepackage[nolist,smaller]{acronym}
\usepackage{nomencl}
\usepackage[style=long,nolist]{glossaries}

\title*{Deciding to Disclose: A Decision Theoretic Agent Model of Pregnancy and Alcohol Misuse}
\author{Jonathan Gray \and Jakub Bijak \and Seth Bullock\\
University of Southampton, Southampton, SO17 1BJ, United Kingdom\\
E-mail: \texttt{j.gray@soton.ac.uk}}
\date{\vspace{-5ex}}
\begin{document}
\maketitle

%*************************
% Acronyms
%*************************
%\phantomsection
%\refstepcounter{dummy}
%\pdfbookmark[1]{Acronyms}{acronyms}
%\markboth{\spacedlowsmallcaps{Acronyms}}{\spacedlowsmallcaps{Acronyms}}
%\section*{Acronyms}
\begin{acronym}[UML]
  \acro{FAS}{Foetal Alcohol Syndrome}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{PT}{Prospect Theory}
  \acro{NICE}{National Institute for Health and Care Excellence}
  \acro{IAPT}{Improving Access to Psychological Therapies}
  \acro{CMACE}{Centre for Maternal and Child Enquiries}
  \acroindefinite{CMACE}{the}{the}
  \acro{AUDIT}{Alcohol Use Disorders Identification Test}
  \acro{T-ACE}{Tolerance, Annoyance, Cut down, Eye-opener}
  \acro{RCOG}{Royal College of Obstetricians and Gynecologists}
  \acroindefinite{RCOG}{the}{the}
  \acro{AML}{acute myeloid leukemia}
  \acro{ADHD}{Attention Defecit Hyperactivity Disorder}
  \acro{PND}{Postnatal Depression}
  \acro{RCT}{randomised control trial}
  \acro{WHO}{the World Health Organisation}
  \acro{ESS}{Evolutionarily Stable Strategy}
  \acrodefplural{ESS}[ESS]{Evolutionarily Stable Strategies}
  \acro{MCMC}{Markov chain monte carlo methods}
  \acro{DU}{Discounted Utility}
  \acro{AIC}{Akaike information criterion}
  \acro{ANOVA}{analysis of variance}
  \acro{ALSPAC}{the Avon Longitudinal Study of Parents and Children}
  \acro{GEM}{Gaussian Emulation Machine}
  \acrodefplural{GEM}{Gaussian Emulation Machines}
  \acro{GEM-SA}{Gaussian Emulation Machine for Sensitivity Analysis}
  \acro{JIT}{Just-in-time}
  \acro{ABM}{Agent Based Modelling}
  \acro{ABMs}{Agent Based Models}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{FFH}{Fast and Frugal Heuristic}
  \acro{OFC}{orbito-frontal cortex}
  \acro{BACCO}{Bayesian Analysis of Computer Code Outputs}
  \acro{IQR}{interquartile range}
\end{acronym}

@@

%\refstepcounter{dummy}
%\pdfbookmark[1]{Glossary}{glossary}
%\printglossary[type=main]

%\printnomenclature{}

@@

\input{Abstract}
\acresetall

\input{Introduction} %(half page)

\input{Background}

\input{Model}

\input{Methods}

\input{Results}

\input{Conclusion}
\input{Acknowledgements}

\bibliography{library,library_addendum}
\bibliographystyle{spbasic}

\appendix
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\input{SensitivityAnalysis}
\end{document}
